Industrial Best Practice

### 2015-03-22 ibp/ibp.tex
typos fixed

Exhaustive research has found that there exists very few similar soultions similar to our own. While there are countless books related to the subject [!!!list some?], very few actually aim to address the needs of busniness and customers; they are primarily focused on the developer.

%Examples of similar products
Apiary is a popular online API design service. Apiary focuses on a collaborative approach to creating APIs, the tool offers the ability to work with between 5 and 50 contributors on a single project. The unique part of this tool is that it provides a "mock" API by which customers, developers or anyone with access can work with. This stage allows quick prototyping and testing of an API before any real coding has taken place. The tool, while useful, doesn't aim to solve the problem of handling changes to APIs but is instead a good platform to quickly prototype ideas.

Mashery provide a more business oriented approach to API development. They offer a wide variety of services with API management being one of them. Quoting their website, they:

@@

>>>>

Exhaustive research has found that there exists very few similar solutions similar to our own. While there are countless books related to the subject [!!!list some?], very few actually aim to address the needs of business and customers; they are primarily focused on the developer.

%Examples of similar products
\subsection{Related Products}
% http://apiary.io/products
Apiary is a popular online API design service. Apiary focuses on a collaborative approach to creating APIs, the tool offers the ability to work with between 5 and 50 contributors on a single project. The unique part of this tool is that it provides a "mock" API by which customers, developers or anyone with access can work with. This stage allows quick prototyping and testing of an API before any real coding has taken place. The tool, while useful, doesn't aim to solve the problem of handling changes to APIs but is instead a good platform to quickly prototype ideas. Apiary also includes some Github integration adding to it's already strong collaboration tools.

%http://www.mashery.com
Mashery provide a more business oriented approach to API development. They offer a wide variety of services with API management being one of them. Quoting their website, they:

@@

%http://swagger.io/
Swagger 2.0 is another online design tool for APIs. Swagger has the added bonus of including a "Generator" for creating some basic library code for users to build upon. Swagger, online Apiary, is primarily used for RESTful APIs. Similarly to the previously mentioned companies, Swagger is more of a tool solution rather than a guideline or framework.
